\chapter{Design}
\label{Chapter:Design}

This chapter discusses the design considerations taken during the design development of the system. The design stage is very important since it lays down the foundation for the whole system.
Thus a considerable amount of time has been spent in designing the system. \citet[12]{bell2005} states that about 5\% of the total time that takes for the development of a software should be spent for the design state alone. For comparison, the coding process takes about 7\%; Testing takes 8\%. 

The design process has gone through many iterations to ensure the best possible quality of the product. The research presented in chapter \ref{Chapter:Literature-Review} has affected immensely the design, especially section \ref{section:commercial-har-systems}. The design can be split into two main sections, namely User Interface (UI) Design and System Architecture (SA) design.

    \section{UI Design}
    TO BE DONE
    
    \section{Architecture Design}
    This section discuses the design of the system on a software level.
    
        \subsection{Mobile Platform and IDE}
        The first point that was considered on a software level was the \textbf{mobile platform} on which the proposed application will be implemented and distributed. After research on the current market, Google's \textit{Android} was fount to dominate the market in Europe \citep{williams2016}. Android-based smartphones hold 75.6\% of market share dominating other mobile platforms such as Apple's \textit{iOS} and Microsoft's \textit{Windows Phone}. Thus, Android was chosen to form the basis of for the proposed mobile application since it potentially will allow the application to be downloaded and used by as many people as possible.
        
        After choosing the mobile platform, one important decision is to choose the development environment or the \textbf{Integrated Development Environment} (\gls{ide}) that will be used to develop the application. That was an easy decision since Android Studio is known to be the official \gls{ide} for Android development \citep{androidstudio2017}.