\chapter{Survey results}
\label{chapter:survey-results}
\centering
\ \fontsize{9}{12}\selectfont
\tabulinesep=1mm
\begin{longtabu} to \textwidth {|l|l|l|}
\hline
    No
    & \textbf{Question}
      \textbf{Response}
    & \textbf{Response summary}
    \endhead \hline
    1
    & What is your age?
    & 18 to 24 (100\%)
    \\ \hline
    2
    & \makecell[l]{Were you more active then usual (e.g. walking, running)\\ as a result of using ActiveMinutes?}
    & \makecell[l]{Yes (33.33\%)\\ No (33.33\%)\\  Not sure (33.33\%)}
    \\ \hline
    3 
    & \makecell[l]{When notified for prolonged inactivity (e.g. 30 minutes of inactivity),\\ did you try to do at least 5 minutes of physical activity?}
    &\makecell[l]{Yes (66.67\%)\\ No (0\%)\\  Sometimes (33.33\%)}
    \\ \hline
    4
    & \makecell[l]{Does seeing past days goal-performance (e.g. in the History screen)\\motivate you to achieve a goal?}
    & \makecell[l]{Yes (100\%)\\ No (0\%)\\  Not sure (0\%)}
    \\ \hline
    5
    & \makecell[l]{Does the visual feedback (i.e. the green progress bar) encourage\\ you to achieve your goal?}
    & \makecell[l]{Yes (100\%)\\ No (0\%)\\  Somewhat (0\%)}
    \\ \hline
    6
    & \makecell[l]{Do you think the application was accurate when measuring your\\ activity levels?}
    & \makecell[l]{Yes (66.67\%)\\ No (0\%)\\  Somewhat (33.33\%)}
    \\ \hline
    7
    & \makecell[l]{How easy to understand was the user interface of the application?\\ (0 being very difficult and 100 being very easy)}
    & \makecell[l]{85}
    \\ \hline
    8
    & \makecell[l]{Was the mobile application battery-friendly?}
    & \makecell[l]{Yes (66.67\%)\\ No (0\%)\\  Somewhat (33.33\%)}
    \\ \hline
\end{longtabu}
\newpage
\begin{longtabu} to \textwidth {|l|l|l|}
\hline
    No
    & \textbf{Question}
      \textbf{Response}
    & \textbf{Response summary}
    \endhead \hline
    9
    & \makecell[l]{Do you have any suggestions regarding \\the mobile application in general?}
    & \makecell[l]{(1) "Great application, I like the feature\\ that notifies you when you have been inactive for \\a certain amount of time. The application could maybe \\have a feature to alert you when you should go to bed to\\ achieve the best amount of sleep. For future development,\\ the application could maybe sync with a watch."\\ \\
    (2) "Slightly wider ranges in terms of sleep time\\ and active and inactive minutes and perhaps\\ a more obvious "Key" informing the users as to what each\\ bar in the history means.\\ Otherwise really easy to use."\\ \\
    (3) "The application could be improved in \\the future by optimising it to be more battery-friendly."}
    \\ \hline
\end{longtabu}