\chapter{Usability Testing}
\label{chapter:usability-testing}

\fontsize{9}{12}\selectfont
    \tabulinesep=1mm
  \begin{longtabu} to \textwidth {|l|X|X|l|}
    \hline
      \textbf{Task No}
      & \textbf{Task}
      & \textbf{Comments}
      & \textbf{Status}
    \endhead \hline
    1
    & \raggedright Open the application and create an account.
    & \raggedright The user was able to understand what was required and complete the process by accessing the Sign-up screen, entering their credentials and selecting the \textit{SIGN UP} button.
    & Pass
    \\ \hline
    2
    & \raggedright Navigate to the \textit{Today} screen.
    & \raggedright The user was able to navigate to the screen by accessing the navigational drawer and selecting the \textit{Today} text label.
    & Pass
    \\ \hline
    3
    & \raggedright Navigate to the \textit{Today} screen and describe what you are seeing.
    & \raggedright The user was able to explain correctly the purpose of the screen i.e., the screen shows the current activity and inactivity goals as well as their progress
    & Pass
    \\ \hline
    4
    & \raggedright Navigate to the \textit{History} screen.
    & \raggedright The user was able to navigate to the screen by accessing the navigational drawer and selecting the \textit{History} text label.
    & Pass
    \\ \hline
    5
    & \raggedright Navigate to the \textit{History} screen and describe what you are seeing.
    & \raggedright The user was able to explain correctly the purpose of the screen i.e., the screen shows past goal-performance in both representations \textit{Daily} and \textit{Weekly}. 
    
    \textbf{Note:} It took the user a bit more time to associate the \gls{pa} and \gls{mci} text labels with the two progress bar for each list item.
    & Pass
    \\ \hline
    6
    & \raggedright  Navigate to the \textit{History} screen; switch to \textit{Daily} view of the list and select a day from the list.
    & \raggedright The user was able to perform the task without any signs of confusion.
    & Pass
    \\ \hline
    7
    & \raggedright After selecting a list item in task 6, explain what you are seeing on the screen.
    & \raggedright The user was able to correctly explain what information the dialog window was showing.
    & Pass
    \\ \hline
    8
    & \raggedright Navigate to the \textit{History} screen, switch to \textit{Weekly} view of the list and explain what you are seeing.
    & \raggedright The user was able to correctly explain the information shown on the screen.
    & Pass
    \\ \hline
    9
    & \raggedright When task 8 is completed, select an item from the list and explain what you are seeing. 
    & \raggedright The user was able to correctly explain what information the dialog window was showing.
    & Pass
    \\ \hline
    10
    & \raggedright Navigate to the \textit{Settings} screen and explain what you are seeing.
    & \raggedright The user was able to navigate to the screen without any signs of confusion and correctly explain the purpose of the screen (i.e. provide access to personalising the functionality of the application).
    & Pass
    \\ \hline
    11
    & Navigate to the \textit{Settings} screen and change the physical activity goal.
    & \raggedright The user was able to successfully change the goal by selecting the \textit{Physical Activity goal} from the list and selecting a value from the dialog window.
    & Pass
    \\ \hline
    12
    & Navigate to the \textit{Settings} screen and change the sedentary goal.
    & \raggedright The user was able to successfully change the goal by selecting the \textit{Sedentary goal} from the list and selecting a value from the dialog window.
    & Pass
    \\ \hline
    13
    & Navigate to the \textit{Settings} screen and change the \textit{Sleeping Hours} time interval.
    & \raggedright The user was able to successfully change the time interval by setting the appropriate \textit{From} and \textit{To} values from the dialog date picker.
    & Pass
    \\ \hline
    14
    & Navigate to the \textit{Settings} screen and switch off the inactivity notifications.
    & \raggedright The user was able to successfully turn off the inactivity notifications by tapping on the check box next to the \textit{Notify me when I am inactive} settings item.
    & Pass
    \\ \hline
    15
    & Log out of the application.
    & \raggedright The user was able to log out of the system by accessing the navigational drawer and selecting the \textit{Log Out} button.
    & Pass
    \\ \hline
    16
    & Log in to the application
    & \raggedright The user was able to log in to the system by opening the application, typing their credentials and selecting the \textit{LOG IN} button.
    & Pass
    \\ \hline
\end{longtabu}