\chapter{Use cases}
\label{use_cases}
\section*{Log in}
    The user opens the application. The system shows the log-in screen. The user types in their username and password. If the provided credentials are valid, the system shows the main screen of the application.
    
\section*{Sign up}
    The user opens the application and go to the Sign-up screen. The system shows the Sign-up screen and opening the virtual keyboard awaiting user input. The user enters their username and password. The system verifies that the entered information is correct and creates a new user account. The user is taken to the main screen of the application.
    
\section*{Set \gls{pa} goal}
    The user opens the application. The system takes the user to the main screen. The user opens the navigation drawer and selects the \textit{Settings} menu item. The system opens the Settings screen. The user selects the "Physical Activity goal" settings item. The system shows a dialog window with list of options. The user selects the desired option. The system accepts the user input and updates the system accordingly.

\section*{Change \gls{sb} remind interval}
    The user opens the application. The system takes the user to the main screen. The user opens the navigation drawer and selects the \textit{Settings} menu item. The system opens the Settings screen. The user selects the "\textit{Notify inactivity}" settings item. The system shows a dialog window providing list of options. The user selects the remind interval and confirms their choice by pressing the "OK" button. The system accepts the user input and updates the system accordingly. 
    
\section*{Change \textit{"Sleeping Hours"}}
    The user opens the application. The system opens the main screen. The user opens the navigation drawer and selects the \textit{Settings} menu item. The system opens the Settings screen. The user selects the "\textit{Sleeping Hours}" settings item. The system shows a date picker dialog. The user selects the preferred time interval and confirms their choice by pressing the "OK" button. The system accepts the user input and updates the system accordingly.
    
\section*{Check goal progress}
    The user opens the application. The system opens the main screen (i.e. \textit{Today} screen). The user sees the amount of \gls{pa} in minutes as well as the previously set goal. The user closes the application.
    
\section*{Check activity history}
    The user opens the application. The system shows the main screen. The user opens the navigation drawer and selects the \textit{"History"} settings item. The system opens the History screen. The user sees the history of activities softed either \textit{"Daily"} or \textit{"Weekly"}. The user closes the application. 